---
title: "R Notebook"
output: html_notebook
---

---
title: "Counterfactual Testing Associational Model"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

```{r, message=FALSE}
# clear the working space
rm(list = ls())

library(here)
library(stats) # need this to calculate Mahalanobis Distance
library(parallel) # parallelize
library(dplyr)
library(FNN)
library(cluster)
library(ggplot2)
library(rpart)
library(caret)
```

# Counterfactual Data Input
```{r}
# we need the renaming function for cleaning
melor_2015 <- read.csv(here("data", "clustered_M15_CF_data2.csv"))
```



# Counterfactual

## Importing trained models
```{r}
# Read the .rds models
base_reg <- readRDS(here("associational XGBOOST", "damage_fit_reg_base.rds"))
trunc_reg <- readRDS(here("associational XGBOOST", "trunc_damage_fit_reg.rds"))
clas_model  <- readRDS(here("associational XGBOOST", "ass_XGBOOST_class.rds"))
```

## Counterfactual predictions
```{r}
source(here("R", "ass_hurdle_function.R"))

# setting threshold for classification step
threshold = 0.30

preds <- ass_hurdle_function(df = melor_2015, ass_clas_model = clas_model,
  ass_base_model = base_reg, ass_trunc_model = trunc_reg ,threshold = threshold)
```

```{r}
# append the results to the counterfactual dataset
melor_2015  <- melor_2015 %>%
    mutate(damage_preds = preds)
```

## Counterfactual results

```{r}

# convert the Cluster column to factor
melor_2015$Cluster <- as.factor(melor_2015$Cluster)

# extract cluster_levels
cluster_levels <- levels(melor_2015$Cluster)

# Source function: counterfactual_results 
source(here("R", "counterfactual_results.R"))


cf_results <- counterfactual_results(cf_data = melor_2015, 
                                     cluster_levels = cluster_levels) 


```


```{r}
# Check the list to confirm plots are stored
print(cf_results$plots)
```

```{r}
print(cf_results$median)
```

```{r}
print(cf_results$averages)
```


# Output the counterfactual predictions
Saving the counterfactual predictions for mapping differences  between this 
associational model with in QGIS.

```{r eval=FALSE}
# prep

CF_output <- melor_2015 %>%
  select(Mun_Code, damage_preds) %>%
  rename(ass_CF_M15 = damage_preds)
  
write.csv2(CF_output, file = here("associational XGBOOST", "ass_CF_M15.csv"))
```

# OLD CODE

```{r, eval=FALSE, echo=FALSE}
# plots_list  <- list()
# means_list  <- list()
# median_list  <- list()
# 
# for (i in seq_along(mun_clusters)) {
#   # Get the current entry
#   current_entry <- mun_clusters[[i]]
# 
#   # Convert the nested list entry to a data frame format
#   plot_data <- bind_rows(lapply(names(current_entry), function(region) {
#     data.frame(Mun_Code = unlist(current_entry[[region]]), island_regions = region, stringsAsFactors = FALSE)
#   }))
# 
#   # Merge with original data to get predicted damage
#   merged_data <- melor_2015 %>%
#     inner_join(plot_data, by = "Mun_Code")
# 
#   # Create boxplot
#   p <- ggplot(merged_data, aes(x = island_groups, y = damage_preds, fill = island_groups)) +
#     geom_boxplot() +
#     labs(title = paste("Predicted Damage Distribution - List Entry", i),
#          x = "Island Region",
#          y = "Predicted Damage") +
#     theme_minimal()
# 
#  # Save the plot in the list
#   plots_list[[i]] <- p
# 
#   # Calculate the mean of damage_preds for each island_groups
#   mean_values <- merged_data %>%
#     group_by(island_groups) %>%
#     summarise(mean_damage = mean(damage_preds, na.rm = TRUE))
# 
#   # Save the means in the list
#   means_list[[i]] <- mean_values
# 
#  # Calculate median of the damage_preds for each island groups
#   median_values  <- merged_data %>%
#     group_by(island_groups) %>%
#     summarise(median_damage = median(damage_preds, na.rm = TRUE))
# 
#   # save the medians in the list
#    median_list[[i]]  <- median_values
# 
# }
# 
# # Check the list to confirm plots are stored
# print(plots_list)
```





